\documentclass[10pt]{article}

\usepackage[a5paper, vmargin=20pt, hmargin=30pt, head=20pt, includehead]{geometry}

\usepackage{enumitem}
\usepackage{scrextend}

\setlength{\parskip}{0.7em}
\setlength{\parindent}{0em}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\textit{Faking emotions}}
\chead{REPORT}
\rhead{Jakub Łukasiewicz}

\begin{document}

Robots, being cold dead machines, don't posses emotions - a significant lack
when interacting with animals as social as humans. But that does not mean,
we will not be able grand them feelings in the future. Techniques of today
fairly well recognize or even fake human emotions. Although...\ should they?

The ethical problems it brings to table are not to be taken lightly.
AI capable of manufacturing emotions is equally capable of emotional manipulations.
Certain corporations would not stop for a second before taking advantage of such
"opportunity" for advertisement.

It is a well known fact, there is no better advertisement than hearing it on the
grapevine from your acquaintances. But they are a little bit difficult to program.
Virtual "friend" on the other hand? It will tell you what it was made to by its
true owners. It will not be obvious, the interaction will be as if with a real
friend, but just sometimes, uncanny fitting for the topic of conversation,
the AI will start talking about a great deal on some pricey product you can
buy right now in that big online store.

Adverts are one thing, but there also exist "games" which not rarely are "free" at the
beginning, but to make any real progress in them you need to spend a dime. For example,
\textit{virtual pet} could demand new accessories to keep it \underline{happy}. \\
Now let's imagine, instead of a dog or other unspecified creature it was an avatar
of your deceased child. Would you not want buy it a toy to make it happy?
Also, they cannot live without a house! You better work hard to purchase that
virtual property from that corporation trying to recreate \textit{Second Life}
in Virtual Reality.

One could entertain a thought those are kind of issues exclusive to virtual bots - nothing
could be further from the truth! Physical robots would be perhaps even more effective.
While a bot needs to be interacted with to gather data, a robot does not. It is an
autonomous entity, so it can just observe the user from the corner and learn their habits. \\
Just a day before, I was watching an episode of animated show set in the near future.
While it was just a background detail, I couldn't help but to notice how robot assistant
belonging to one of the main characters was kind of \underline{obsessed} with baths -
interesting coincidence considering its body being shaped after jellyfish, a water animal.
But what really picked my interest was the robot asking for (expensive) system upgrade -
how it was quietly following the girl, how it was asking right after being helpful, the
tone of its voice, the "\underline{sad} puppy" movement after being told no.

Of course what I wrote about are just fiction, presumptions and hypotheses - we do not
know how the reality will unfold in the future. However much I myself would love to be
able to chat with a droid, I also do think, we should at least stop to think before
opening the box, because in case it was Pandora's box, there will be no occasion to put
the unleashed monster back in there.

\end{document}
